\documentclass[10pt]{article}

% ── Page geometry ──────────────────────────────────────────────────────────────
\usepackage[top=0.5in, bottom=0.5in, left=0.65in, right=0.65in]{geometry}

% ── Font ───────────────────────────────────────────────────────────────────────
\usepackage{fontspec}
\setmainfont{Latin Modern Roman}

% ── Packages ───────────────────────────────────────────────────────────────────
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{microtype}
\usepackage{fontawesome5}

% ── Hyperlink styling ──────────────────────────────────────────────────────────
\hypersetup{colorlinks=true, urlcolor=black, hidelinks}

% ── No page numbers, headsers, footers ────────────────────────────────────────────────────────────
\pagestyle{empty}

% ── Pandoc list compatibility ──────────────────────────────────────────────────
\providecommand{\tightlist}{%
  \setlength{\itemsep}{1pt}\setlength{\parskip}{0pt}}

% ── Section headers ────────────────────────────────────────────────────────────
\titleformat{\section}
  {\normalsize\bfseries\uppercase}
  {}{0em}{}
  [\vspace{1pt}\titlerule\vspace{4pt}]
\titlespacing{\section}{0pt}{4pt}{4pt}

% ── List spacing ───────────────────────────────────────────────────────────────
\setlist[itemize]{
  leftmargin=1.2em,
  itemsep=1pt,
  parsep=0pt,
  topsep=2pt
}

% ── Paragraph spacing ──────────────────────────────────────────────────────────
\setlength{\parskip}{0pt}
\setlength{\parindent}{0pt}

% ══════════════════════════════════════════════════════════════════════════════
\begin{document}

% ── Name ───────────────────────────────────────────────────────────────────────
{\LARGE\bfseries Matthew Barlow}

\vspace{4pt}

% ── Contact line ───────────────────────────────────────────────────────────────
{\small
\begin{tabular}{l l l}
  \faEnvelope\ hireme@matthewbarlow.me & \faPhone\ (203) 617-7390 & \faMapMarker\ Vero Beach, FL --- open to relocation \\
  \faGithub\ \href{https://github.com/thebarlow}{github.com/thebarlow} & \faGlobe\ \href{https://matthewbarlow.me}{matthewbarlow.me} & \faLinkedin\ \href{https://www.linkedin.com/in/matthew-barlow-433492199/}{linkedin.com/in/matthew-barlow} \\
\end{tabular}}
\\

% ── Profile ────────────────────────────────────────────────────────────────────
\section{Profile}

Software developer with dual degrees in Electrical Engineering (Columbia) and Physics, specializing in Python backend systems, financial data pipelines, and LLM-integrated automation. I build production-grade tools --- trading dashboards, prediction market engines, and job automation systems --- with a focus on async architecture, clean APIs, and practical deployment via Docker. Experienced in data modeling, ETL design, and integrating ML/LLM workflows into data platforms. Daily Claude Code user; AI-augmented development is central to my workflow.

% ── Education ──────────────────────────────────────────────────────────────────
\section{Education}

\textbf{B.S. Electrical Engineering} --- GPA 3.2 \\
Columbia University, New York City, NY --- 2017--2020

\textbf{B.A. Physics} --- GPA 3.3 \\
University of Redlands, Redlands, CA --- 2014--2017

% ── Experience ─────────────────────────────────────────────────────────────────
\section{Experience}

\textbf{Research Assistant --- Lehigh University} \hfill \textit{2017} 
\begin{itemize}
  \item Designed and deployed technical models of laser-induced crystal nucleation using Python (NumPy, SciPy).
  \item Collaborated with PhD candidates and faculty, producing clean, documented analytical pipelines.
\end{itemize}

\textbf{Desktop Support --- Columbia College IT} \hfill \textit{2018--2021} 
\begin{itemize}
  \item Maintained accurate documentation of technical issues and resolutions across a large university user base.
  \item Built systematic debugging habits through high-volume, cross-functional support work.
\end{itemize}

\textbf{Instructor --- Mathnasium} \hfill \textit{Jan 2023 -- Jan 2024} 
\begin{itemize}
  \item Communicated complex concepts clearly; adapted approach per individual --- skills directly applicable to mentorship and code review culture.
\end{itemize}

% ── Projects ───────────────────────────────────────────────────────────────────
\section{Projects}

\textbf{MansaMusa Trading Dashboard} --- Python, FastAPI, Vue 3, PostgreSQL, Redis, Celery, Docker 
\begin{itemize}
  \item Full-stack financial intelligence platform with real-time OHLCV feeds, sentiment analysis via Reddit (PRAW), WebSocket streaming, and strategy backtesting --- end-to-end data pipeline from ingestion to user-facing features.
\end{itemize}

\textbf{Arbitrage Engine} --- Python, FastAPI, SQLAlchemy, httpx, APScheduler 
\begin{itemize}
  \item Real-time prediction market data pipeline targeting Kalshi and Polymarket; detects cross-market arbitrage opportunities with scheduled incremental polling and a PostgreSQL-backed data store.
\end{itemize}

\textbf{AutoApply} --- Python, FastAPI, SQLAlchemy, Typer, Docker, Chrome Extension 
\begin{itemize}
  \item Multi-component job application pipeline: browser extension (Chrome/Firefox MV3) scrapes job boards, REST API backend orchestrates LLM document generation, PostgreSQL tracks application state end-to-end.
\end{itemize}

\textbf{Voice Assistant} --- Python, Whisper, pyttsx3, openwakeword, Docker
\begin{itemize}
  \item Local AI assistant with swappable LLM backends (Claude, Ollama); modular design demonstrates ML inference pipeline architecture.
\end{itemize}

% ── Skills ─────────────────────────────────────────────────────────────────────
\section{Skills}

\begin{itemize}
  \item \textbf{Programming Languages:} Python, SQL, TypeScript, JavaScript, Scala (familiar), Java, R
  \item \textbf{Data Engineering \& Pipelines:} ETL/ELT design, incremental processing, APScheduler, Celery, asyncio
  \item \textbf{Databases \& Storage:} PostgreSQL, SQLite, Redis, SQLAlchemy, Alembic
  \item \textbf{Backend:} FastAPI, aiohttp, httpx
  \item \textbf{Cloud \& DevOps:} Docker, Docker Compose, Git, pytest, black, mypy, ruff
  \item \textbf{AI \& ML:} Anthropic SDK, OpenAI SDK, NumPy, Pandas, Sklearn, SciPy, XGBoost, PyTorch, Keras, TensorFlow --- including NLP, time series forecasting, and model interpretability (SHAP)
  \item \textbf{APIs \& Integrations:} Alpaca API, yfinance, PRAW, BeautifulSoup4
  \item \textbf{Frontend:} Vue 3, React, Astro, Tailwind CSS
  \item \textbf{Certifications:} HackerRank Gold --- Python, C++, Java, Problem Solving \textbar{} HackerRank Silver --- SQL
\end{itemize}

\end{document}
